---
title: "Assignment 3"
author: "Teague Tran"
date: "2/27/2021"
output: html_document
---

Link to folder: https://github.com/teaguetran/ESM262_A1a/tree/master/Assignment_3_Teague_Tran

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(usethis)
source("calculate_density.R")
source("density_comparison.R")
source("num_lowdensity.R")
```

What I am trying to do: 

Calculate the density of liquids d= m/V; determine if the liquid is more/less/equally as dense compared to water. There will be three functions to get the job done: calculate_density(), density_comparison(), and density_while_loop()

For calculate_density(): 

@param mass of liquid (g)
@param volume of liquid (mL)
@param density threshold is 1 g/mL

For density_comparison():
@param density of liquid (g/mL)
@param density threshold = 1 g/mL

For density_while_loop():
@param density of liquid (g/mL)
@param density threshold = 1 g/mL

```{r}

#check the code to see if they work
densities <- calculate_density(c(1,2,4,5,6,3,4,9,9,10), c(4,5,3,3,2,3,4,5,4,9))

density_comparison(d = densities)

num_lowdensity(d = densities)
```




